Scaling of Electrode-Electrolyte Interface Model Parameters In Phosphate Buffered Saline

### 2014-01-13 paper.tex
Update paper.tex
Added more comments to reviewers comments

{\color{blue}
I am not very enthusiastic about his paper as it does not contain many novel or original ideas and finding. On the electrochemistry side it is superficial and falls back behind published state of the art and textbook knowledge.\\
{\color{OliveGreen} Our response}\\

1. The interface model as such is not new and has been published extensively.\\
{\color{OliveGreen} Our response}\\

2. The authors do not at all comment on interface polarization, which is particularly important under DC conditions. As soon as an electrode carries current, such phenomena become important and relevant.\\
{\color{OliveGreen} Our response}\\

3. To assess the resistivity or impedance of a material between two electrodes, one normally uses a 4-electrode setup with injection of current through the two outer electrodes, while measuring a voltage between the inner ones. This is particularly relevant for the measurements in Fig. 3 and the related and subsequent text.\\
{\color{OliveGreen} Our response}\\

4. The authors never mention the origin of any Faradaic contribution at the electrodes. What is the electro- or redox-chemistry that the authors assume to happen?? Gas formation at the electrodes, electrolysis of the saline, i.e., hydrogen and oxygen formation??\\
{\color{OliveGreen} Our response}\\

5. Figure 5 is not referenced anywhere in the text. Also the blue variations in the curves are hardly visible.\\
{\color{OliveGreen} Our response}\\

6. Since the electrode model includes two back-to-back diodes, I think it would be valuable to sweep the voltage from -1.2V to +1.2V.\\
{\color{OliveGreen} Our response}\\

7. There is a big difference between blue dots and red curve in Fig. 10, except for the "voltage increment time" and "64 seconds after increment".  This indicates to me that the CPE model is NOT that accurate, as the settling curve is highly correlated to the CPE parameters.\\
{\color{OliveGreen} Our response}\\
}

@@

{\color{blue}
In this manuscript, the authors report how the non-linear electrode-electrolyte interface model parameters change as a function of saline solution concentration. This is a very interesting and important subject that could be potentially of great importance for readers of IEEE Transactions on Biomedical Circuits ans Systems. The manuscript is well written and adequately referenced. However, the reviewer would like to pose a few questions to the authors to clarify some  issues in the manuscript, which should be addressed.\\
{\color{OliveGreen} Our response}\\

page 2, in text/ table II. The scaling parameters and their meanings should be described more comprehensively. They remain somewhat unclear and meaningless to reader.\\
{\color{OliveGreen} Our response}\\

page 2 Measurement of the CPE. What was the current density used in EIS measurements?
What is the effect of chosen current density on CPE impedance (Fig. 5)?
In addition,  measurement apparatus information is fully lacking.\\
{\color{OliveGreen} Our response}\\

>>>>

{\color{blue}
I am not very enthusiastic about his paper as it does not contain many novel or original ideas and finding. On the electrochemistry side it is superficial and falls back behind published state of the art and textbook knowledge.\\
{\color{OliveGreen}
    {\color{Red} Research textbook knowledge and published state of the art relating to electro chemistry in our area.}
    No response yet.
}\\

1. The interface model as such is not new and has been published extensively.\\
{\color{OliveGreen} 
    {\color{Red} Review and discuss existing interface models}
    No response yet.
}\\

2. The authors do not at all comment on interface polarization, which is particularly important under DC conditions. As soon as an electrode carries current, such phenomena become important and relevant.\\
{\color{OliveGreen}
    {\color{Red} Is polarisation a separate mechanism from double layer formation? If so, can we address? Polarisation will be just as important in cyclic measurement techniques where the cycle time is low. Does anyone understand polarisation sufficiently to remove it from measurements? Is polarisation not just remaining charge in a layer around an electrode, is it not just the double layer?}
    No response yet.
}\\

3. To assess the resistivity or impedance of a material between two electrodes, one normally uses a 4-electrode setup with injection of current through the two outer electrodes, while measuring a voltage between the inner ones. This is particularly relevant for the measurements in Fig. 3 and the related and subsequent text.\\
{\color{OliveGreen} 
    {\color{Red} I don't understand what use doing this would be. All voltage dropped between two end electrodes, voltage proportional to total impedance between electrodes. The most use you could get from this would be to find how much is dropped across a single interface, which is exactly what we are doing.}
    No response yet.    
}\\

4. The authors never mention the origin of any Faradaic contribution at the electrodes. What is the electro- or redox-chemistry that the authors assume to happen?? Gas formation at the electrodes, electrolysis of the saline, i.e., hydrogen and oxygen formation??\\
{\color{OliveGreen}
    {\color{Red} My assumption is that we don't give a crap what it is, whatever it is, we're modelling it. If you want to know that, look elsewhere.}
    No response yet.
}\\

5. Figure 5 is not referenced anywhere in the text. Also the blue variations in the curves are hardly visible.\\
{\color{OliveGreen} 
    {\color{Red} Enhance color variation in Figures 4 and 5 and make a reference to Figure 5}
    No response yet.
}\\

6. Since the electrode model includes two back-to-back diodes, I think it would be valuable to sweep the voltage from -1.2V to +1.2V.\\
{\color{OliveGreen}
    {\color{Red} The diodes are identical, this is moving into polarisation territory again. In effect, they are both being used (one by + and other by -). I don't know what to say about this. We wanted to make all the measurements happen in as little time as possible. We have data from sweeps in the other direction, not DC though.}
    No response yet.
}\\

7. There is a big difference between blue dots and red curve in Fig. 10, except for the "voltage increment time" and "64 seconds after increment".  This indicates to me that the CPE model is NOT that accurate, as the settling curve is highly correlated to the CPE parameters.\\
{\color{OliveGreen}
    {\color{Red} This is true, try and pinpoint exactly why this is happening. Why does the CPE perform so well in the CPE frequency response plots yet so poorly in the Faradaic part?}
    No response yet.
}\\
}

@@

{\color{blue}
In this manuscript, the authors report how the non-linear electrode-electrolyte interface model parameters change as a function of saline solution concentration. This is a very interesting and important subject that could be potentially of great importance for readers of IEEE Transactions on Biomedical Circuits ans Systems. The manuscript is well written and adequately referenced. However, the reviewer would like to pose a few questions to the authors to clarify some  issues in the manuscript, which should be addressed.\\

page 2, in text/ table II. The scaling parameters and their meanings should be described more comprehensively. They remain somewhat unclear and meaningless to reader.\\
{\color{OliveGreen}
    {\color{Red} Pull in more explination from JonathanScott2013 relating to the resistor mesh}
    No response yet.
}\\

page 2 Measurement of the CPE. What was the current density used in EIS measurements?
What is the effect of chosen current density on CPE impedance (Fig. 5)?
In addition,  measurement apparatus information is fully lacking.\\
{\color{OliveGreen}

}\\
